---
title: "Project"
author: "Nagarjuna sricharan Maram & Shardul Jani"
date: "6 December 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE , message = FALSE)
```

```{r}
#install.packages("tseries")
library(tseries)
#install.packages("readxl")
library(readxl)
#install.packages("forecast")
library(forecast)
#install.packages("ggplot2")
library(ggplot2)
#install.packages("tseries")
library(tseries)
#install.packages("Metrics")
library(Metrics)
#install.packages("TSA")
library(TSA)
```


$$Department\ 94$$

```{r}
D94 <- read_excel("C:/Users/Charan/Desktop/Fall 17/Data Mining/Project/D94.xlsx")
```

```{r}
D94$Month <- as.Date(D94$Month)
```

```{r}
d94 <- D94[,-3]
```

```{r}
covariate94 <- D94[1:25,3]
```


```{r}
d94.train <- d94[1:25,1:2]
d94.test <- d94[26:33,1:2]
```

#Arima

#Time series plot
```{r}
library(ggplot2)
ggplot(D94 , aes(Month , Sale)) + geom_line() 

```


#Test for stationary
```{r}
 adf.test(diff(diff(d94.train$Sale)))
```

```{r}
acf(d94.train$Sale)
```

```{r}
pacf(d94.train$Sale)
```

```{r}
Model94.A <- stats::arima(d94.train$Sale , order = c(3,2,2))
Model94.A
```

```{r}
tsdiag(Model94.A)
```

```{r}
predict94.1 <- forecast(Model94.A , n.ahead = 8)
plot(predict94.1)
```

```{r}
rmse(d94.test$Sale, predict94.1$mean)
```

#ARIMAX
```{r}
arimax94.A <- arimax(d94.train$Sale , order =  c(3,2,2) ,xtransf =  covariate)
predict94.2 <- predict(arimax94.A , n.ahead = 8)
 rmse(d94.test$Sale , predict94.2$pred)

```



# Average method
```{r}
predict94.3 <- meanf(d94.train$Sale , h =8)

rmse(predict94.3$mean , d94.test$Sale)

```

```{r}
plot(predict94.3)
```



#Naive method
```{r}
 predict94.4 <- naive(d94.train$Sale , h =8)
 rmse(predict94.4$mean , d94.test$Sale)
```

```{r}
plot(predict94.4)
```


#Drift method
```{r}
predict94.5 <- rwf(d94.train$Sale , h = 8 , drift = TRUE)
rmse(predict94.5$mean , d94.test$Sale)


```

```{r}
plot(predict94.5)
```




$$Department\ 92$$

#Load Data
```{r}
D92 <- read_excel("C:/Users/Charan/Desktop/Fall 17/Data Mining/Project/D92.xlsx")

```


```{r}
D92$Month <- as.Date(D92$Month)
```

```{r}
d92 <- D92[,-3]
```

```{r}
covariate92 <- D92[1:25,3]
```

```{r}
d92.train <- d92[1:25,1:2]
d92.test <- d92[26:33,1:2]
```


```{r}
library(ggplot2)
ggplot(D92 , aes(Month , Sale)) + geom_line()
```

#Arima

#Test for stationary
```{r}
adf.test(diff(diff(d92.train$Sale)))

```

```{r}
acf(d92.train$Sale)
```

```{r}
pacf(d92.train$Sale)
```

```{r}
Model92.A <- stats::arima(d92.train$Sale , order = c(2,2,0))
Model92.A
```

```{r}
tsdiag(Model92.A)
```

```{r}
predict92.1 <- forecast(Model92.A , n.ahead = 8)
plot(predict92.1)
```

```{r}
rmse(d92.test$Sale, predict92.1$mean)
```

#Arimax
```{r}
arimax92.A <- arimax(d92.train$Sale , order =  c(2,2,0) ,xtransf =  covariate92)
predict92.2 <-predict(arimax92.A , n.ahead = 8)
 rmse(d92.test$Sale , predict92.2$pred)
```



#Average 
```{r}
predict92.3 <- meanf(d92.train$Sale , h =8)

rmse(predict92.3$mean , d92.test$Sale)
```

```{r}
plot(predict92.3)

```


#Naive
```{r}
 predict92.4 <- naive(d92.train$Sale , h =8)
 rmse(predict92.4$mean , d92.test$Sale)
```

```{r}
plot(predict92.4)
```


#Drift Method
```{r}
predict92.5 <- rwf(d92.train$Sale , h = 8 , drift = TRUE)
rmse(predict92.5$mean , d92.test$Sale)
```

```{r}
plot(predict92.5)
```

$$Department\ 38$$

#Loading dataset 
```{r}
D38 <- read_excel("C:/Users/Charan/Desktop/Fall 17/Data Mining/Project/D38.xlsx")
```

```{r}
D38$Month <- as.Date(D38$Month)
```

```{r}
d38 <- D38[,-3]
```

```{r}
covariate38 <- D38[1:25,3]
```

```{r}
d38.train <- d38[1:25,1:2]
d38.test <- d38[26:33,1:2]

```

#Time series plot
```{r}
library(ggplot2)
ggplot(D38 , aes(Month , Sale)) + geom_line() 
```

#Arima

#Test for stationary

```{r}
adf.test(d38.train$Sale)

```

# 
```{r}
acf(d38.train$Sale)

```

#
```{r}
pacf(d38.train$Sale)

```

#
```{r}
Model38.A <- stats::arima(d38.train$Sale , order = c(0,0,1))
Model38.A
```

#
```{r}
tsdiag(Model38.A)
```

#
```{r}
predict38.1 <- forecast(Model38.A , n.ahead  = 8)
plot(predict38.1)

```
#
```{r}
rmse(d38.test$Sale, predict38.1$mean)

```

#Arimax
```{r}
arimax38.A <- arimax(d38.train$Sale , order =  c(0,0,1) ,xtransf =  covariate38)
predict38.2 <-predict(arimax38.A , n.ahead = 8)
rmse(d38.test$Sale , predict38.2$pred)

```

#Average method
```{r}
predict38.3 <- meanf(d38.train$Sale , h =8)

rmse(predict38.3$mean , d38.test$Sale)
```

```{r}
plot(predict38.3)
```


#Naive
```{r}
predict38.4 <- naive(d38.train$Sale , h =8)
 rmse(predict38.4$mean , d38.test$Sale)

```

```{r}
plot(predict38.4)
```

#Drift method
```{r}
predict38.5 <- rwf(d38.train$Sale , h = 8 , drift = TRUE)
rmse(predict38.5$mean , d38.test$Sale)

```

```{r}
plot(predict38.5)
```


$$ Department\ 95$$

```{r}

D95 <- read_excel("C:/Users/Charan/Desktop/Fall 17/Data Mining/Project/D 95.xlsx")

```

```{r}
D95$Month <- as.Date(D95$Month)

```


```{r}
d95 <- D95[,-3]

```

```{r}
covariate95 <- D95[1:25,3]

```

```{r}
d95.train <- d95[1:25,1:2]
d95.test <- d95[26:33,1:2]

```


#time series plot

```{r}
library(ggplot2)
ggplot(D95 , aes(Month , Sale)) + geom_line()

```

 

#Arima


#test for stationary
```{r}
adf.test(diff(diff((d95.train$Sale))))

```


#
```{r}
acf(d95.train$Sale)
```

#
```{r}
pacf(d95.train$Sale)

```


#

```{r}
Model95.A <- stats::arima(d95.train$Sale, order = c(0,0,0))
Model95.A

```

#
```{r}
tsdiag(Model95.A)

```


#
```{r}
predict95.1 <- forecast(Model95.A , n.ahead = 8)
plot(predict95.1)
```



#
```{r}
rmse(d95.test$Sale, predict95.1$mean)
```







#Average Method
```{r}
predict95.3 <- meanf(d95.train$Sale , h =8)

rmse(predict95.3$mean , d95.test$Sale)
```

```{r}
plot(predict95.3)

```



#Naive Method
```{r}
predict95.4 <- naive(d95.train$Sale , h =8)
rmse(predict95.4$mean , d95.test$Sale)
```

```{r}
plot(predict95.4)

```


#Drift Method

```{r}
predict95.5 <- rwf(d95.train$Sale , h = 8 , drift = TRUE)
rmse(predict95.5$mean , d95.test$Sale)

```

```{r}
plot(predict95.5)
```



$$Department/ 90$$

# for dept 90

```{r}
D90 <- read_excel("C:/Users/Charan/Desktop/Fall 17/Data Mining/Project/D 90.xlsx")
```

```{r}
D90$Month <- as.Date(D90$Month)

```

```{r}
d90 <- D90[,-3]

```

```{r}
covariate90 <- D90[1:25,3]

```

```{r}
d90.train <- d90[1:25,1:2]
d90.test <- d90[26:33,1:2]
```


#time series plot

```{r}
library(ggplot2)
ggplot(D90 , aes(Month , Sale)) + geom_line() 
```

#Arima

#test for stationary

```{r}
adf.test(diff((d90.train$Sale)))

```


#
```{r}
acf(d90.train$Sale)

```


#
```{r}
pacf(d90.train$Sale)

```


#
```{r}
Model90.A <- stats::arima(d90.train$Sale , order = c(0,1,0))
Model90.A
```

#
```{r}
tsdiag(Model90.A)

```


#
```{r}
predict90.1 <- forecast(Model90.A , n.ahead = 8)
plot(predict90.1)
```

#
```{r}
rmse(d90.test$Sale, predict90.1$mean)

```




#Average Method
```{r}
predict90.3 <- meanf(d90.train$Sale , h =8)

rmse(predict90.3$mean , d90.test$Sale)
```

```{r}
plot(predict90.3)

```


#Naive Method
```{r}
predict90.4 <- naive(d90.train$Sale , h =8)
rmse(predict90.4$mean , d90.test$Sale)
```

```{r}
plot(predict90.4)

```


#Drift Method
```{r}
predict90.5 <- rwf(d90.train$Sale , h = 8 , drift = TRUE)
rmse(predict90.5$mean , d90.test$Sale)
```

```{r}
plot(predict90.5)

```

#Based on the above results, we have chosen different forecasting methods for different departments based on the RMSE error.

#Department 94 - Arima 
#Department 92 - naive
#Department 38 - Drift
#Department 95 - Arima
#Department 90 - naive



#lets forecast future values of 4 months for the above departments.

#Department 94

```{r}
adf.test(diff(diff(d94$Sale)))
```

```{r}
acf(d94$Sale)
```

```{r}
pacf(d94$Sale)
```

```{r}
Model1 <- stats::arima(d94$Sale , order = c(2,2,1))
Model1
```

```{r}
tsdiag(Model1)
```

```{r}
predict1 <- forecast(Model1 , n.ahead = 4)
predict1$mean
```

```{r}
plot(predict1)
```

#Department 92
```{r}
predict2 <- naive(d92$Sale , h = 4)
predict2
```

```{r}
plot(predict2)
```

#Department 38
```{r}
predict3 <- rwf(d38$Sale , h = 4 , drift = TRUE)
predict3$mean

```

```{r}
plot(predict3)
```


#Department 95

```{r}
adf.test(diff(diff(d95$Sale)))
```

```{r}
acf(d95$Sale)
```

```{r}
pacf(d95$Sale)
```

```{r}
Model4 <- stats::arima(d95$Sale , order = c(0,0,0))
Model4
```

```{r}
tsdiag(Model4)
```

```{r}
predict4 <- forecast(Model4 , n.ahead = 4)
predict4$mean
```

```{r}
plot(predict1)
```

#Department 90

```{r}
predict5 <- rwf(d90$Sale , h = 4 , drift = TRUE)
predict5$mean

```

```{r}
plot(predict5)
```















































